### 2022-06-28 chapters/optimization/java-dir/java.tex
add : extention to JAVA

\section{Experimental Protocol}\label{sec:javameth}
To investigate the effect that could have the JVM distribution choice and/or parameters on software energy consumption, we conducted a wide set of experiments on a cluster of machines and using several established Java benchmarks and JVM configurations.

@@

@@

\section{Tools and contributions}
\Cref{table:j-referral} illustrates an example of the final report of \textsf{J-Referral}.
The tool was tested for 2 real Java projects: \textsf{Zip4J} and\footnote{\url{https://github.com/srikanth-lingala/zip4j}} and \textsf{K-nucleotide}.\footnote{\url{https://benchmarksgame-team.pages.debian.net/benchmarksgame/performance/knucleotide.html}}.
\textsf{Zip4J} runs a large file compression, while \textsf{K-nucleotide}  extracts a DNA sequence, and updates a hashtable of k-nucleotide keys to count specific values.
The short report presented in \Cref{table:j-referral} shows the ratio of potential energy saving between the most and least energy consuming tested JVM (40\% and 70\% energy savings for \textsf{Zip4J} and \textsf{K-nucleotide} respectively).
Options are available for \textsf{J-Referral} to obtain much more detailed reports including execution time, DRAM usage, split DRAM vs. CPU consumption, etc.
The tool is available as \emph{open-source software} (OSS) from our anonymous repository.\footnote{\url{https://anonymous.4open.science/r/jreferral/Readme.md}}

>>>>

\section{Experimental Protocol}\label{sec:javaprotocol}
To investigate the effect that could have the JVM distribution choice and/or parameters on software energy consumption, we conducted a wide set of experiments on a cluster of machines and using several established Java benchmarks and JVM configurations.

@@

\subsection{Extension}
We also added an extension to the protocol to allow the user to run the same experiment with different configurations. The package is available in the github repository \footnote{\url{https://github.com/chakib-belgaid/jvm-comparaison}}.
To add extra \textbf{candidates} for the benchmark applications, we added a new configuration file \texttt{jvm.sh} in the root directory of the repository, where we put the name and the version of the jvm to be used. 
\note{The jvm must be provided by sdkman\footnote{\url{https://sdkman.io/}}}
For the \textbf{workload},the benchmarks should be provided in the \texttt{benchmarks} directory.
As for extra \textbf{metrics} One can create a new script file that monitor the experiment and record the metrics. We provide some examples such as \texttt{recordpower.sh} to measure the instantanious power and \texttt{recordthreads.s} to measure the number of active threads during the experiment.

For faster experements we propose \textbf{Jreferral}\footnote{\url{https://github.com/chakib-belgaid/jreferral}} an open source that provides an opensource to compare the energy consumption of differents jvms for any java application. Later we will discuss this tool in the section \ref{section:SummaryofContributions}

@@

\section{Tools and contributions}
\Cref{table:j-referral} illustrates an example of the final report of \textsf{J-Referral}.
The tool was tested for 2 real Java projects: \textsf{Zip4J} and\footnote{\url{https://github.com/srikanth-lingala/zip4j}} and \textsf{K-nucleotide}.\footnote{\url{https://benchmarksgame-team.pages.debian.net/benchmarksgame/performance/knucleotide.html}}.
\textsf{Zip4J} runs a large file compression, while \textsf{K-nucleotide}  extracts a DNA sequence, and updates a hashtable of k-nucleotide keys to count specific values.
The short report presented in \Cref{table:j-referral} shows the ratio of potential energy saving between the most and least energy consuming tested JVM (40\% and 70\% energy savings for \textsf{Zip4J} and \textsf{K-nucleotide} respectively).
Options are available for \textsf{J-Referral} to obtain much more detailed reports including execution time, DRAM usage, split DRAM vs. CPU consumption, etc.
The tool is available as \emph{open-source software} (OSS) from our anonymous repository.\footnote{\url{https://github.com/chakib-belgaid/jreferral}}
